---
title: ' Consensus Clustering'
author: Zijian
date: '2020-05-03'
slug: consensus-clustering
categories:
  - bioinformatics
tags:
  - Education
  - Tutorial
---
# Consensus clustering

Consensus Clustering  is a method that provides quantitative evidence for determining the number and membership of possible clusters within a dataset, such as microarray gene expression.This method has gained popularity in cancer genomics, where new molecular subclasses of disease have been discovered.

# The Consensus Clustering method 

it involves subsampling from a set of items,
such as microarrays, and determines clusterings of specified cluster counts (k).
Then, pairwise consensus values, the proportion that two items occupied the
same cluster out of the number of times they occurred in the same subsample,
are calculated and stored in a symmetrical consensus matrix for each k

# Code
```{r message=FALSE}
library(ALL)
data(ALL)
d=exprs(ALL)
d[1:5,1:5]
```


```{r}
#筛选前5000标准差的基因
mads=apply(d,1,mad)
d=d[rev(order(mads))[1:5000],]
```


```{r}
#sweep函数减去中位数进行标准化
d = sweep(d,1, apply(d,1,median,na.rm=T))
```


```{r}
#一步完成聚类
library(ConsensusClusterPlus)
title=tempdir()
results = ConsensusClusterPlus(d,maxK=6,reps=50,pItem=0.8,pFeature=1, title=title,clusterAlg="hc",distance="pearson",seed=1262118388.71279,plot="png")

#consensusMatrix - the consensus matrix.
# #For .example, the top five rows and columns of results for k=2:
results[[2]][["consensusMatrix"]][1:5,1:5]
```
```{r}
results[[2]][["consensusTree"]]
```

```{r}
results[[2]][["consensusClass"]][1:5]
```

```{r}
icl <- calcICL(results, title = title,plot = "png")
icl[["clusterConsensus"]]
```

